Reading Notes

### 2020-08-31 2pd.tex
commenting out some moved stuff that i'll delete maybe later?

Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost effective solar power.
%% espinosa 2013
The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
Multijuction cells may achieve efficiencies that surpass this limit, but they often do not have lower energy payback times as their production is more costly.
\autoref{nrel} shows the efficiency gains made by single junction silicon and organic photovoltaic devices over the last 30 years.
These are merely a selection among the many categories of PV devices.
The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{(a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
\end{wrapfigure}
Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
In 2018, a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.

@@

Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.

@@

The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
\subsection*{Molecular Dynamics}

>>>>

Organic photovoltaics (OPVs, see~\autoref{opv}) are a focus of this research because they represent the best opportunity for cost effective solar power.
The theoretical efficiency limit (Shockley-Queisser limit) for a p-n single junction solar cell is about 30\%\cite{Shockley1961}.
Multijuction cells may achieve efficiencies that surpass this limit, but they often do not have lower energy payback times as their production is more costly.
\autoref{nrel} shows the efficiency gains made by single junction silicon and organic photovoltaic devices over the last 30 years.
These are merely a selection among the many categories of PV devices.
The trend of the silicon cells shows that the efficiency gain is levelling off as the devices approach the Shockley-Queisser limit.
OPV devices, however, still have a lot of room for improvement, and recent increases in efficiency reflect this.
\begin{wrapfigure}{l}{0.5\linewidth}
    \centering
    \includegraphics[width=\linewidth]{images/dou-miller2018c-fig.pdf}
    \caption{(a) roll to roll printing process for OPVs, (b) example OPV device, (c) bulk heterojunction structure, and (d) OPV energy generation process. Part (a) adapted from ref~\cite{Dou2013}. Parts (b,c,d) adapted from ref~\cite{Miller2018c}.}\label{opv}
\end{wrapfigure}
Many of the latest advancements in OPV technology have been through specialized processing or combinations of new chemistries.
One new chemical moiety which has recieved attention is the ladder backbone structure seen in many non-fullerene acceptors (NFAs), see \autoref{chemistries}.
In 2018, a single junction cell using an NFA achieved a record-breaking 13.25\% efficiency\cite{raynergy}.
And in 2019, a cell using an NFA functionalized with chlorine groups was found to achieve 16.5\% efficiency\cite{Cui2019}. 
Ultimately, the efficiency of a solar cell depends on the self-assembly of its active layer.

@@

%Renewable energy accounted for 11\% of the U.S. energy consumption in 2019 and of that 9\% was from solar (approximately 1\% of the total energy)\cite{USEIA2020}.
%However, our energy infrastructure has room for improvement: consider Germany which in 2019 got 43\% of its energy from renewables and 8.2\% of its total energy from solar\cite{Wirth2017}.

@@

%The atomic and electronic properties are important for light absorption, in which an exciton is created, and charge transfer, where the exciton is dissociated into a free electron and hole\cite{Scharber2006a,Hoppe2004,Mazzio2015}.
%At the same time, the exciton finding an interface at which to dissociate and the separated charges finding a path to an electrode both depend on the morphology of the active layer.
\subsection*{Molecular Dynamics}
